### 2012-05-11 GUIErrorDetector/paper/evaluation.tex
add 1 sentence to the limitation section. saying we missed 1 error found by jsr308.
add a link to the bug reports

%After checking against existing patches, we found
%Our tool correctly identified the \oldbugs known errors, as compared to
%their patches.
We submitted all \newbugs new errors
to the respective developers. As of April 2012, 
we have reproduced 3 errors, the S3dropbox developers have confirmed
1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
have not yet been verified by the developers.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
This variant ran out of memory on all subjects, and did not output any real
errors before it terminated.  The number of
non-cyclic paths in a graph is exponential in the graph size, and it 
it is infeasible to enumerate all paths
for a realistic call graph, which often contains thousands of nodes.
%only a very few amount of paths can be enumerated within a practical amount of time.

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
search strategy is one that reports some error-revealing path between
E and U, while an unsound strategy might report a non-error-revealing
path between the nodes (Figure~\ref{fig:ex} shows an example).
Exhaustive search is sound because it does not
miss any possible (non-cyclic) paths.  However, it is impractical.
BFS and DFS are unsound because they visit
every node, but do not traverse every \emph{path} path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.

>>>>

We submitted all \newbugs new errors
to the respective developers. As of April 2012, 
we have reproduced 3 errors, the S3dropbox developers have confirmed
1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
have not yet been verified by the developers. All found bugs
and the tool's output are publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.

%for a realistic call graph consisting of thousands
%of nodes,

%only a very few amount of paths can be enumerated within a practical amount of time.

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
search strategy is one that reports some error-revealing path between
E and U, while an unsound strategy might report a non-error-revealing
path between the nodes (Figure~\ref{fig:ex} shows an example).
Exhaustive search is sound because it does not
miss any possible (non-cyclic) paths.  However, it is impractical.
BFS and DFS are unsound because they visit
every node, but do not traverse every path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
